---
title: "Class 14: Social Movements online, in effect, dying out, and going forward"
subtitle: "Contemporary social movements and beyond: climate, migration"
author: "[Dr. Michael C. Zeller](https://michaelzeller.de)"
format: 
  rladies-revealjs:
    footer: ""
    slide-number: c/t
    toc: TRUE
    toc-depth: 1
    toc-title: Agenda for the day
    menu: TRUE
    theme: [default, custom_options]
    background-transition: fade
incremental: false
embed-resources: true
# runtime: shiny
bibliography: ../../../library.bib
---

# Opening notes {background-color="#2c844c"}

::: {.tenor-gif-embed data-postid="14209777" data-share-method="host" data-aspect-ratio="1.94" data-width="70%"}
<div class="tenor-gif-embed" data-postid="14209777" data-share-method="host" data-aspect-ratio="1.94" data-width="100%"><a href="https://tenor.com/view/open-gif-14209777">Open Sticker</a>from <a href="https://tenor.com/search/open-stickers">Open Stickers</a></div> <script type="text/javascript" async src="https://tenor.com/embed.js"></script> 
:::

```{=html}
<script type="text/javascript" async src="https://tenor.com/embed.js"></script>
```

## Presentation groups

<!-- ::: panel-tabset -->
<!-- ## December -->

| Date    | Presenters                       | Method |
| -------:|:---------------------------------|:------:|
| 4 Dec:  | Daichi, Seongyeon, Jehyun        | ethnography | 
| 8 Jan:  | Ayla, Tara, Theresa, Annabelle   | discourse analysis | 
| 15 Jan: | Luna, Emilene, Raffa, Sofia      | TBD    | 

: Presentations line-up

<!-- | 11 Dec: |                                  | TBD    |  -->


<!-- ## January -->

<!-- | Date    | Presenters                       | Method | -->
<!-- | -------:|:---------------------------------|:------:| -->
<!-- | 15 Jan: | Luna, Emilene, Raffa             | TBD    |  -->

<!-- : Presentations line-up -->

<!-- | 8 Jan:  |                                  | TBD    |  -->
<!-- | 22 Jan: |                                  | TBD    |  -->
<!-- | 29 Jan: |                                  | TBD    |  -->

<!-- ::: -->

<!-- []{style="font-size:10px;"} -->

<!-- For a course on 'social movements' and a class meeting on 'social movements demobilization' (i.e., the decline and end of movements), can you suggest some discussion questions to ask students? Ideally, the questions should have multiple choice responses, or yes/no/maybe responses, or strongly agree/agree/disagree/strongly disagree responses? -->


# Klausur instructions and brief review {background-color="#2c844c"}

:::: {.columns}
:::{.column width="50%"}
- exam-day instructions 
- quick review of Vorlesung material, themes: 
    1. historical experience 
    2. Constitutional Court 
    3. parliamentary system, executive dominance 
    4. cooperative federalism 
    5. elections, parties, and party system change

:::

::: {.column width="50%"}
<div class="tenor-gif-embed" data-postid="16633244770639601466" data-share-method="host" data-aspect-ratio="1.5748" data-width="100%"><a href="https://tenor.com/view/you-can-do-it-reminder-gif-16633244770639601466">You Can Do It Reminder GIF</a>from <a href="https://tenor.com/search/you+can+do+it-gifs">You Can Do It GIFs</a></div> <script type="text/javascript" async src="https://tenor.com/embed.js"></script> 
:::
::::

## Klausur instructions

- [2 February (Monday) at (promptly!) 8.00]{style="color:red;"} in the [AudiMax](https://www.lmu.de/raumfinder/#/building/bw0000/map?room=000000100_)

. . . 

- arrive at [7.45]{style="color:red;"} to get checked in 
- bring your ID!
- consider going to the toilet before entering Audimax... 

## Klausur instructions 

- time management: e.g., 15 minutes each for 3 Vorlesung questions; 45 minutes for 1 essay question
- FIVE questions provided --- THREE must be answered
- Questions consist of **[factual]{style="color:cadetblue;"}** knowledge component and **[analytical]{style="color:cadetblue;"}** component
- Overview of central topics in the lecture plan (under '*Organisatorisches*'). Exam questions relate to these central topics
- Reference to central articles of the Basic Law relevant for some questions (e.g. Eternity clause Art. 79, Paragraph 3 of the Basic Law; Art. 21 bz Regulation of parties)
- details about other countries are not required knowledge

## Quick review of Prof. Bolleyer’s course material

- **FIVE themes in the Vorlesung course**
    1. Germany as system shaped by [historical experience]{style="color:forestgreen;"}
    2. Federal [Constitutional Court]{style="color:violet;"} as above day-to-day politics vs. strategic actor (Vanberg model)
    3. Germany classified as [parliamentary system]{style="color:teal;"} that invites executive dominance
    4. Germany classified as case of [cooperative federalism]{style="color:purple;"} 
    5. [Elections, parties, and party system change]{style="color:goldenrod;"}

## 1. Germany as system shaped by history - basics

1. Constitutional state based on fundamental rights & parliamentary representative democracy 
2. Designed for [power sharing/taming the power]{style="color:forestgreen;"} of the executive
3. [“Semi-sovereign” state]{style="color:forestgreen;"} – democratic principle restricted by constitutionality/court
4. [Central role of the parties]{style="color:forestgreen;"}; simultaneously multi-party system (numerous “veto players”)
5. State of [grand coalitions]{style="color:forestgreen;"}: tension between party competition and cooperation pressures (federalism)
6. [“Delegating state”]{style="color:forestgreen;"} (e.g. collective bargaining, central bank)
7. “Open state” [transfer of sovereignty]{style="color:forestgreen;"} (EU) --> elements counteract the concentration of power in the executive

## 1. Germany as system shaped by history {.smaller}

- Lessons from Weimar: e.g., Eternity clause Art. 79 Abs. 3
- Areas of focus: 
    (1) [constitutional principle vs. democratic principle]{style="color:forestgreen;"} (BRD: constitutional sovereignty, UK: parliamentary sovereignty); 
    (2) [substantive vs. procedural understanding of democracy]{style="color:forestgreen;"} (different from the Weimar Constitution)
- Key concept: *[wehrhafte Demokratie]{style="color:forestgreen;"}*
    + “defensive democracy” --> intended to prevent democracy from abolishing itself through democratic procedures
    + e.g., [Eternity clause]{style="color:forestgreen;"}; [forfeiture of basic rights]{style="color:forestgreen;"} (Art. 18 GG); [group ban]{style="color:forestgreen;"} (Art. 9 Abs 2 GG); [party ban]{style="color:forestgreen;"} (Art. 21 Abs 2 GG); constitutional protection offices; officials’ [duty to be loyal]{style="color:forestgreen;"} to the constitution (Article 5, 33 GG)
- Logic of [consensus democracy]{style="color:forestgreen;"}: gov. responsive to as many citizens as possible; maximal interests integrated into decision-making process --> prevent tyrannous majority


## 2. Federal [Constitutional Court]{style="color:violet;"} 

- [independence of BVerfG]{style="color:violet;"} as sign of separation of powers (checks and balances): “guardian of the constitution”; appointment of judges, required qualifications of judges
- Forms of (self-)limitation
    1. how [political context influences whether the BVerfG]{style="color:violet;"} declares laws unconstitutional (*abstract norm control*)
    2. Court relies on [enforceability]{style="color:violet;"} and [acceptance]{style="color:violet;"} 
    3. Court tend to exercise [restraint in times of crisis]{style="color:violet;"} (e.g. Corona)
    4. Legislators [can change the organisation and resources]{style="color:violet;"} of the court (with a simple majority, no Federal Council veto)
    5. Legislators can change rules by [amending the constitution]{style="color:violet;"}
    6. Federal Constitutional Court only takes [action after a lawsuit]{style="color:violet;"}

## 3. Germany: [parliamentary system]{style="color:teal;"}, executive dominance

::: {style="margin-top: -40px;"} 
- [separation of powers]{style="color:teal;"} (less helpful to understand exec.-leg. relation in parliamentarism --- different in presidentialism)
- Primary characteristic of parliamentarism: dependence of the executive on the legislature 
    + result: [functional interlocking of powers]{style="color:teal;"} - government & government majority/factions dominate legislation (“interlocking” also through the government’s right of initiative)
    + opposition factions exercise '[control rights]{style="color:teal;"}'
- Central institutional mechanisms: 
    + [election of the chancellor]{style="color:teal;"} (chancellor majority)
    + [confidence vote]{style="color:teal;"} and [constructive vote of no confidence]{style="color:teal;"} – promotes stability (cf. Weimar!)

::: 

## 4. Germany classified as case of [cooperative federalism]{style="color:purple;"} {.smaller}

- Cooperative federalism in Germany (vs. dual federalism/separate federalism (e.g. USA))
    + Essentially an executive federalism ([state governments in the Bundesrat]{style="color:purple;"} influence the national constitution, implementation of laws by state administrations centrally)
    + [Distribution of powers that encourages cooperation]{style="color:purple;"}: e.g. competing legislation; community tasks; also: financial integration (community taxes) (vs. clear “separation” in dual/separate federalism)
    + Article 72, Paragraph 2 of the Basic Law “[establishment of equal living conditions in the federal territory]{style="color:purple;"}” (“unitary federalism”) --> Political integration also through voluntary, horizontal cooperation: Conferences of Ministerpräsidenten

- Bundesrat - strong second chamber: legislative power of consent
    + Composition: [government representatives of the states]{style="color:purple;"} (unlike the classic Senate model)

## 5. [Elections]{style="color:goldenrod;"}, parties, and party system change

- **Political participation**: *all activities that citizens do voluntarily with the goal to influence the political system*
    + [conventional]{style="color:goldenrod;"} (e.g., voting) vs. [unconventional]{style="color:goldenrod;"} (e.g., protesting)
        * [trend towards individual participation]{style="color:goldenrod;"} forms---away from collective forms (societal changes such as individualisation, secularisation)
    + Voting/elections are central form of participation
        * [responsiveness mechanism]{style="color:goldenrod;"} (according to voter preference) --> increasing tension here
        * generates: *[legitimation]{style="color:goldenrod;"}*, *[mobilisation]{style="color:goldenrod;"}*, *[recruitment]{style="color:goldenrod;"}*, *[representation]{style="color:goldenrod;"}*, etc.

## 5. Elections, [parties]{style="color:goldenrod;"}, and party system change

- **Parties**: *political groups that present candidates for public office* (Sartori 1976/2000)
    + parties as "[transmission belts]{style="color:goldenrod;"}" (like interest groups), but operate in society and within political institutions
    + in DE, parties are '[institutional actors]{style="color:goldenrod;"}' or '[state organs]{style="color:goldenrod;"}' (Art. 21 GG)
    + central aspects: participation in political [decision-making]{style="color:goldenrod;"}; obligation of [intra-party democracy]{style="color:goldenrod;"}; state [financing]{style="color:goldenrod;"} (and accountability); possible party ban

## 5. Elections, parties, and [party system change]{style="color:goldenrod;"} 

::: {style="margin-top: -40px;"} 
- **party system**: *the system of interactions resulting from inter-party competition* (Sartori 1976)
- focus on **[new 'players']{style="color:goldenrod;"}** in the system or on **[system characteristics]{style="color:goldenrod;"}**
- context: established parties face challenges (shrinking membership, sinking trust, greater vote competition from newcomers [Grüne, AfD, BSW], new cleavages)
- relevant system elements:
    + [format]{style="color:goldenrod;"}: number of parties
    + [fragmentation]{style="color:goldenrod;"}: parties relative size/strength
    + [content]{style="color:goldenrod;"}: policy/ideological position of a parties
    + [polarisation]{style="color:goldenrod;"}: ideological/policy distance between parties 
    + [segmentation]{style="color:goldenrod;"}: coalition potential of parties

::: 

## Vorlesung: example question {.scrollable} 

["How has political participation in Germany changed over the last four decades and what are the key explanatory factors for this?"]{style="color:indigo; font-size:40px;"} 

[„Wie hat sich politische Partizipation in Deutschland in den letzten vier Jahrzehnten gewandelt und was sind zentrale Erklärungsfaktoren dessen?“]{style="font-size:16px;"}

- Remember: questions consist of **factual** knowledge component and **analytical** component
    + no Pro/Contra discussion -- not enough time
- Here, **political participation** is the key concept (*factual knowledge*)
    + what does it mean? Explain it briefly in your answer
    + Discuss briefly: less party participation; expansion of participation forms (e.g., protests, petitions); emergence of online participation --> more individualised participation, less collective
- Causes for these changes (*analytical knowlege*)
    + secularisation (less religious adherence), expansion in education, change in values, technological innovations (for digital participation) --> all favour more individual participation, less collective

# Pointers on research papers {background-color="#2c844c"}

:::: {.columns}
:::{.column width="50%"}
- basics of a good paper: 
    + introduction 
    + main body 
    + conclusion 
- golden rules for any paper

:::

::: {.column width="50%"}
<div class="tenor-gif-embed" data-postid="16527898" data-share-method="host" data-aspect-ratio="1.78771" data-width="100%"><a href="https://tenor.com/view/kermit-the-frog-typing-busy-typewriter-writing-gif-16527898">Kermit The Frog Typing GIF</a>from <a href="https://tenor.com/search/kermit+the+frog-gifs">Kermit The Frog GIFs</a></div> <script type="text/javascript" async src="https://tenor.com/embed.js"></script> 
:::
::::

## Basics of a good paper - introduction 

- [What?]{style="color:cadetblue;"}
    + What is the *[puzzle]{style="color:red;"}* or *[research question]{style="color:red;"}*?
    + There are two types of questions: **interesting** questions and **researchable** questions --- unfortunately, there is quite limited overlap between them...
        * a main challenge in research is to *find a way to transform a big, interesting question into a researchable one* (this is the intricacy of **research design**)
- [Why?]{style="color:cadetblue;"} Theoretical, methodological, and/or practical relevance
- [How?]{style="color:cadetblue;"} Structure of the argument/paper
- About 10% of entire paper

## Basics of a good paper - main body

- Case selection
    + Which cases (what population)? When? Why?
    + Scope conditions
- Phenomenon of interest
    + Definitions $\rightarrow$ systematised concepts $\rightarrow$ indicators/operationalisation $\rightarrow$ data source
    + specify what kind of data you will use and where it comes from
- For descriptive analysis
    + Consider creating a typology/multi-dimensional concept
- For causal analysis: potential causes of your DV/outcome
    + theories, hypotheses, and causal mechanisms

## Basics of a good paper - conclusion

- Brief summary of argument (and findings)
- What is it that you are NOT saying and investigating?
- Future research
- Maximum 10% of text

## Golden rules for any paper

::: {style="margin-top: -40px;"} 
- Structure: paper should have a structure which is 
    + clear, summarised in introduction, explicit as the paper unfolds
    + One paragraph = one idea
    + Help your reader: (i) sum up a section, (ii) link to/justify next section
- Answer the question you have chosen:
    + a tragic mistake is to give a brilliant answer to a question that is subtly different to the one you asked
- Writing:
    + words have precise meanings, use them with care---they are the tools of the scholarly trade!
    + KISS (keep it simple, stupid): clear words; short sentences

::: 

# Summarising and moving forward {background-color="#2c844c"}

:::: {.columns}
:::{.column width="50%"}
- SMs in the round: big course take-aways 
- movements of the future: migration-related and climate-related

:::

::: {.column width="50%"}
<div class="tenor-gif-embed" data-postid="1882214034414119125" data-share-method="host" data-aspect-ratio="1.36066" data-width="100%"><a href="https://tenor.com/view/synthesis-gif-1882214034414119125">Synthesis GIF</a>from <a href="https://tenor.com/search/synthesis-gifs">Synthesis GIFs</a></div> <script type="text/javascript" async src="https://tenor.com/embed.js"></script> 
:::
::::

## SMs in the round: big course take-aways

[movements are [integral to modern democracies]{style="color:goldenrod;"}, and many other systems/societies]{style="font-size:45px;"}

. . . 

[movements are [shaped by the context (POS)]{style="color:violet;"} in which they emerge $\rightarrow$ but [movements can reshape context]{style="color:cadetblue;"} (if they are lucky and very successful)]{style="font-size:45px;"}

. . . 

[even *modestly successful* [movements can change how people understand issues (through framing)]{style="color:forestgreen;"} and set the stage for later (more successful) movements]{style="font-size:45px;"} 

## Open data - POLDEM {background-color="#ffe0b2"}

::: panel-tabset
### Visualisation

```{r warning=FALSE, message=FALSE}
library(dplyr)
library(tidyr)
library(lubridate)
library(xts)
library(dygraphs)
library(htmlwidgets)

poldem <- read.csv("../resources/data/poldem/poldem-protest_30.csv", stringsAsFactors = FALSE)
poldem$date  <- as.Date(poldem$date)
poldem$month <- floor_date(poldem$date, "month")

env_events  <- poldem %>% filter(issue_environment == "yes")
xeno_events <- poldem %>% filter(issue_xeno == "yes")

env_monthly  <- env_events  %>% count(month) %>% rename(Environment = n)
xeno_monthly <- xeno_events %>% count(month) %>% rename(Xenophobia = n)

issues_ts <- full_join(env_monthly, xeno_monthly, by = "month") %>%
  arrange(month) %>%
  mutate(across(c(Environment, Xenophobia), ~replace_na(.x, 0)))

issues_xts <- xts(issues_ts[, c("Environment", "Xenophobia")], order.by = issues_ts$month)

dygraph(issues_xts, main = "Environmental vs. xenophobic/anti-immigration protest events over time") %>%
  dySeries("Environment", color = "#1b9e77") %>%
  dySeries("Xenophobia", color = "#d95f02") %>%
  dyRangeSelector(dateWindow = c("2000-01-01", "2015-12-01")) %>%
  dyAxis("x", axisLabelFormatter = JS("function(d){ return d.getFullYear() }")) %>%
  dyLegend(width = 400)

```

### Map

```{r warning=FALSE, message=FALSE}
library(dplyr)
library(sf)
library(mapview)
library(leafpop)
library(maps)

data(world.cities)

city_lookup <- world.cities %>%
  arrange(desc(pop)) %>%
  mutate(name_key = tolower(name)) %>%
  distinct(name_key, .keep_all = TRUE) %>%
  select(name_key, lat, long)

geocode_issue <- function(df) {
  df %>%
    mutate(name_key = tolower(community)) %>%
    filter(!is.na(name_key), !grepl("entire country", name_key)) %>%
    left_join(city_lookup, by = "name_key") %>%
    filter(!is.na(lat))
}

env_geo  <- geocode_issue(env_events)
xeno_geo <- geocode_issue(xeno_events)

env_sf  <- st_as_sf(env_geo,  coords = c("long", "lat"), crs = 4326) %>% st_jitter(amount = 0.02)
xeno_sf <- st_as_sf(xeno_geo, coords = c("long", "lat"), crs = 4326) %>% st_jitter(amount = 0.02)

m_env <- mapview(
  env_sf, color = "#1b9e77", col.regions = "#1b9e77",
  layer.name = "Environmental protests",
  popup = popupTable(env_sf, zcol = c("date", "country_name", "community", "action_form", "part_all"))
)

m_xeno <- mapview(
  xeno_sf, color = "#d95f02", col.regions = "#d95f02",
  layer.name = "Anti-immigration protests",
  popup = popupTable(xeno_sf, zcol = c("date", "country_name", "community", "action_form", "part_all"))
)

m_env + m_xeno

```


### Explanatory note

Data source: Kriesi et al. 2020, [PolDem-Protest Dataset](https://poldem.eui.eu/) 30 European Countries, Version 1. Two subsets, events flagged `issue_environment == "yes"` and events flagged `issue_xeno == "yes"`, plotted as monthly counts against each other, to compare the ebb and flow of environmental vs. xenophobic/anti-immigration mobilisation over the 2000-2015 window (e.g. the latter's rise around the 2015 "refugee crisis" period).


::: 


## UN Global Compact for **Migration** (GCM) 

::: panel-tabset
### UN info video 
<!-- Aspect ratios include 1x1, 4x3, 16x9 (the default), and 21x9. -->
{{< video https://www.youtube.com/watch?v=LL87BK5OSz8 
    start="1"
    aspect-ratio="21x9" 
    width="900" 
    height="525"
>}}

### UN - IOM video
<!-- Aspect ratios include 1x1, 4x3, 16x9 (the default), and 21x9. -->
{{< video https://www.youtube.com/watch?v=HZtOtSR_3f8 
    start="1"
    aspect-ratio="21x9" 
    width="900" 
    height="525"
>}}

### oppositional 'Rebel News' video

[instructor note]{style="color:red;"}: this news outlet consistently represents a [far-right, often Islamophobic perspective](https://firstmonday.org/ojs/index.php/fm/article/view/12546/10700). The video below innacurately portrays the GCM to bolster an editorial narrative (e.g., 'Brexit')

<!-- Aspect ratios include 1x1, 4x3, 16x9 (the default), and 21x9. -->
{{< video https://www.youtube.com/watch?v=J-I8_EyG638 
    start="1"
    aspect-ratio="21x9" 
    width="700" 
    height="425"
>}}

:::


## Migration-related - @rone2023StopPactForeign

- UN Global Compact for **Migration** (GCM)
    + comprehensive treaty covering [international migration]{style="color:cadetblue;"}
- **[Rejection/abstention]{style="color:red;"}** (in order, all second half of 2018) by Hungary, Austria, Czechia, Poland, Slovakia, Italy, Bulgaria, Latvia, Romania
    + [any patterns here?]{style="color:indigo;"}
- **movements and parties** launched a multi-faceted [campaign]{style="color:darkred;"} that generated protest and spurred advocacy networks transnationally
    + movement influence on foreign policy 
        * (rare because foreign policy is supposedly reserve of elite-level politics, but movements do occasionally impact; cf. '[International Campaign to Ban Landmines]{style="color:goldenrod;"}')
    + movement influence on discourse and policy on immigration

## Migration-related - @rone2023StopPactForeign

- four country cases: **Austria, Belgium, Germany, and Italy** (different governing parties and mobilisation on migration)
    + strong anti-GCM campaigns: Germany (helped by AfD and *Junge Alternative* [@heinze2024DriversRadicalisationDevelopment] and movement orgs. like Identitarians), Belgium (*Vlaams Belang* and nationalist youth groups) -- **but ultimately unsuccessful; beaten in parliament**
    + anti-GCM campaign unnecessary: Italy (competitive collaboration between *Lega* and *FdI*)
    + complementary anti-GCM campaign: Austria (movement activity supporting ÖVP and FPÖ government decision)
- **[is it all down to the strength of parliamentary allies?]{style="color:indigo;"}**

## Climate-related - @zhang2023DiffusionDynamicsDigital

::: {style="margin-top: -40px;"} 
- investigating **(informational) diffusion** and **'connective' action** of Germany's FFF using Twitter data
    + retweeting sequences and the following/follower relationships

- [**development** of digitally networked movements **depends on** their **ability to influence and spread among different networked publics**]{style="color:darkorange;"} 
- [right-leaning actors’ attempted to delegitimise]{style="color:darkorange;"} the movement; [left-leaning actors engaged to condemn leading parties]{style="color:darkorange;"} and bring digital politics into the discourse

::: {style="margin-top: -40px;"} 
> [diffusion mechanisms of information, discourses, and beliefs of digitally networked movements were mainly enabled by... preexisting networks rather than situational spontaneity. However, they varied according to issue salience and were distinguished by the network structures, political positions, ideological lines, and geographical proximities of the involved communities]{style="font-size:29px;"} 

::: 

::: 

## Final thoughts and further questions

**Movements in the future** 

. . . 

- intensifying competition of movements and states/targets 

. . . 

- danger of social media companies' self-regulation 

. . . 

- transnationalism of movements (climate movement[s], anti-migration movement[s])

## THANK YOU!

- No class next week -- good luck on your exam!
- Essays (for those not taking Klausur) due **[2026-03-07]{style="color:red;"}**
- Thank you for the feedback on course evaluations: **if you have any follow-ups, please write to me or see me during office hours**

::: {style="text-align: center;"}
[Thanks for coming and being great students!]{style="color:goldenrod; font-size:100px;"} 
::: 

# Any questions, concerns, feedback for this class? {background-color="#2c844c"}

Anonymous feedback here: <https://forms.gle/AjHt6fcnwZxkSg4X8>

Alternatively, please send me an email: [m.zeller\@lmu.de]{style="color:red;"}


```{r echo=FALSE, message=FALSE, warning=FALSE}
pagedown::chrome_print(file.path("..", "docs/slides", "slides_14.html"))
```


## References
