---
title: "Syllabus"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(timeDate)
library(tibble)
library(dplyr)
library(knitr)

# https://www.benlinzmeier.rocks/post/an-rmarkdown-syllabus-template/
# http://svmiller.com/blog/2016/07/r-markdown-syllabus/

library(lubridate) # for submission date of assignments

# library(RefManageR)
# bib <- ReadBib("library.bib")
# myopts <- BibOptions(bib.style = "authoryear", style="latex", first.inits=FALSE, max.names = 20)

# https://www.lmu.de/en/workspace-for-students/abc-study-guide/lecture-periods/index.html
# https://www.ferienwiki.de/feiertage/de/bayern

#This code chunk sets up a table of meeting days for the course.
#You can set days of the week for course meetings (e.g. Monday and Wednesday).
#Semester start and end dates are selected and then university holidays like spring break are specified.
#Days of the week that the course meets. Must be full day name in quotes.
Days <- c("Thursday")
#Semester start date for classes as YYYY/M/D.
SemesterStart <- as.Date("2025/10/16")
#Semester end date for classes as YYYY/M/D.
SemesterEnd <- as.Date("2026/2/7")
#Fall break start and stop date.
WinterBreak <-
  seq.Date(
    from = as.Date("2025/12/22"),
    to = as.Date("2026/1/6"),
    by = "day"
  )
#Spring break start and stop date.
# SpringBreak <-
#   seq.Date(
#     from = as.Date("2022/02/28"),
#     to = as.Date("2022/03/06"),
#     by = "day"
#   )
#Creates a list of days within the semester.
SemesterDays <-
  seq.Date(from = SemesterStart, to = SemesterEnd, by = "day")
#Add day before Thanksgiving.
#Add day before Thanksgiving.
# DayBeforeThnks<-as.Date(holiday(
#     year = getRmetricsOptions("currentYear"),
#     Holiday = c("USThanksgivingDay")))-1
#Full list of holidays that there are no classes including breaks.
Holidays <-
  c(as.Date(holiday(
    year = getRmetricsOptions("currentYear"),
    Holiday = c("USLaborDay", "USMLKingsBirthday")
  )), WinterBreak)
#Create a list of semester days excluding holidays.
SemesterDays <- SemesterDays[!SemesterDays %in% Holidays]
#Make dataframe with all semester days.
ClassDays <- data.frame(index = 1:length(SemesterDays))
#Insert dates.
ClassDays$Date <- SemesterDays
#Insert weekday designation.
ClassDays$Weekday <- weekdays(ClassDays$Date)
#Limit to the class meeting days.
MeetingDays <- ClassDays[ClassDays$Weekday %in% Days, ]
#Create numeric list of weeks.
Week <- cut.Date(MeetingDays$Date, breaks = "week")
levels(Week) <- 1:length(levels(Week))
MeetingDays$Week <- Week
MeetingDays$Class <- 1:nrow(MeetingDays)

Lecture_Topic <- c("Introduction and the development of social movements (SMs)", # Class 1 - (Tarrows intro and chapter 1)
                   "SM theories: collective behaviour, resource mobilisation, political processes", # Class 2
                   "SM theories: framing, civil society", # Class 3
                   "Mobilisation, recruitment, participation", # Class 4
                   "Collective identity and emotions", # Class 5
                   "Organisation, strategies and tactics", # Class 6
                   "SMs and the media", # Class 7 
                   "SM coalitions", # Class 8
                   "State responses", # Class 9
                   "Counter-mobilisation and countermovements", # Class 10
                   "SMs online", # Class 11
                   "SM impact", # Class 12
                   "Demobilisation", # Class 13
                   "Contemporary social movements and beyond: climate, migration", # Class 14
                   "NO CLASS MEETING TODAY") # Class 15"

          
links <- c("#class1","#class2","#class3","#class4","#class5","#class6","#class7","#class8","#class9","#class10","#class11","#class12","#class13","#class14","#class15")

MeetingDays <- bind_cols(MeetingDays, Lecture = Lecture_Topic)
#### Grade table ####
Grades <- tribble( ~ Grade,
                   ~ Range,
                   "A",
                   "90-100",
                   "B",
                   "80-89",
                   "C",
                   "70-79",
                   "D",
                   "60-69",
                   "F",
                   "< 60")
####Assignment weight table####
Weights <- tribble(
                    ~ Item,
                    ~ Weight,
                    "Writing scaffolding",
                    "20 %",
                    "Semester Project",
                    "25 %",
                    "Labratory Assignments",
                    "20 %",
                    "Midterm Exam",
                    "15 %",
                    "Final Exam",
                    "20 %"
                  )
```


<!-- # Recommended prior knowledge -->
<!-- Empfohlene Vorkenntnisse -->

<!-- Students will benefit from familiarity with research literature on political parties, social movements, and/or political violence. But relevant parts of these research fields will be introduced in the course where pertinent.  -->

# Necessary prerequisites
<!-- Notwendige Voraussetzungen -->

Not applicable.

# Course requirements

The examination credit (*Prüfungsleistung*) in this course depends on your degree programme:

```{r requirements, echo=FALSE, message=FALSE, warning=FALSE}
library(kableExtra)
# col1 <- c("","Attendance & Participation","Presentation","Essay"),
kable(data.frame(
  col1 <- c("","BA Hauptfach","BA Nebenfach (60 ECTS)","Lehramt Unterrichtsfach","BA Nebenfach (30 ECTS)", "Lehramt Didaktikfach", "Austauschstudierende für VL", "Austauschstudierende für GK"),
  col2 <- c("Participation","X","X","X","X", "X", "X", "X"),
  col3 <- c("Presentation","","","X","", "", "", "X"),
  col4 <- c("Essay","","","X","", "", "", "X"),
  col5 <- c("Klausur","X","X","X","X (nur VL)", "X (nur VL, 60 Min., 2 Wissensfragen)", "X (nur VL)", "")),
  col.names = NULL, align = c("l","c","c","c","c")) %>%
  kableExtra::kable_styling(bootstrap_options = "bordered") %>% 
  row_spec(1, background = "gold") %>% 
  row_spec(c(3,5,7), background = "pink") %>% 
  row_spec(c(2,4,6,8), background = "cadetblue1") %>% 
  column_spec(1:5, color = "black")
```


```{r requirements1, message=FALSE, warning=FALSE}
#| eval: false
#| include: false
library(kableExtra)
# col1 <- c("","Attendance & Participation","Presentation","Essay"),
kable(data.frame(
  col1 <- c("","Participation","Presentation","Essay","Klausur"),
  col2 <- c("BA main","X","","","X"),
  col3 <- c("BA minor (60 ECTS)","X","","","X"),
  col4 <- c("BA minor (30 ECTS)","X","","","X (nur VL)"),
  col5 <- c("LA Unterrichtsfach","X","X","","X"),
  col6 <- c("Exchange","X","X","X","")),
  col.names = NULL, align = c("l","c","c","c","c","c")) %>%
  kableExtra::kable_styling(bootstrap_options = "bordered") %>% 
  # row_spec(1, background = "seagreen1") %>% 
  row_spec(c(3,5), background = "pink") %>% 
  row_spec(c(2,4), background = "cadetblue1") 

```


## Participation

To receive credit for this course, all students are expected to attend class meetings and participate actively in class discussions. Active participation requires independent preparation, especially [doing the required reading]{style="color:red;"}. Assigned and recommended readings for each session are listed in the [Readings](../schedule/index.qmd).

<!-- ### Expertise on a social movement -->

<!-- Each student participating in the course will choose a contemporary or historical social movement organisation (ideally, one active in Germany) to develop expertise on throughout the term. Students may find it particularly advisable to relate their reading and annotations on Perusall to their chosen social movement organisation. In class discussion, too, students may find it useful to discuss their chosen social movement organisation. -->

<!-- To do this, students will create and maintain a working document in which they summarise (in one or two paragraphs each week) how the topic of the week (for weeks 4-13) relates to their chosen social movement organisation. For example, before our week 4 meeting on '*`r Lecture_Topic[4]`*', a student studying the PEGIDA movement would look at this case and write a short summary about how PEGIDA activists were mostly centred in Dresden and often were older, with experiences of the Montagsdemonstrationen against the DDR regime. By week 13, this student would have a working document of several pages, providing an analytical overview of PEGIDA. -->

<!-- Possible movements organisations in Germany to choose include: Animal Rights Watch (ARIWA), Anti-Nuclear (Anti-Atomkraft) movement, Autonome movement, Demos für Alle, Extinction Rebellion, Federation of Antifascists (VVN-BdA), Fridays for Future, Identitarian movement, Letzte Generation, 'Ohne mich' Bewegung, PEGIDA, Querdenken 711, Sozialistischer Deutscher Studentenbund, Vier Pfoten. -->

## Presentation (*Referat*)

Students that are required by their degree programme to present must give one short (20 minutes maximum) group (2-4 students) presentation of a method of studying social movements. 

A **method** is a system of data collection and analysis. A presentation of a method should introduce the method, explain how (e.g., for what research topics) it is useful for studying social movements, and (most importantly) discuss at least one example of applied research. For example, a group could present *regression analysis* by briefly reviewing the logic of regression techniques, explaining that it is useful for detecting correlations in large sets of data, and explaining how Authors X & Y used regression analysis techniques on protest events within a country.

While students may choose any method after conferring with the instructor, the following is a list of some methods that would be suitable for presentation: linear regression, qualitative comparative analysis (QCA), network analysis, experimental design, content/discourse analysis, quantitative text analysis, process tracing, spatial analysis, ethnography.

Students are responsible for creating their own group and organising their presentation. The date of presentation will be agreed with the instructor and, wherever possible, arranged so that no more than one group presents per class meeting. 

::: {.callout-caution collapse="true"}
## Scoring rubric

```{r pres-rubric, echo=FALSE}
#| message: false
#| warning: false
#| paged-print: false
# Load necessary library
library(dplyr)
library(kableExtra)

rub <- data.frame(
  # block=c("Content", "Content", "Content", "Content", "Form", "Form"),
  criteria=c("<b>1. Introduction</b> <br> - Was the specific method stated? <br> - Were the fundamental concepts necessary for understanding the method explained? <br> - Was it stated what sort of questions/topics the method can address? <br> - Was the sort of data generated/required for the method described? <br> - Was there an overview of the analytical technique(s) of the method?",
             "<b>2. Application to social movements</b> <br> - Was it stated how the method can be applied to social movements questions/topics? <br> - Were (hypothetical or actual) examples discuss of different possible applications?", 
             "<b>3. Applied research example</b> <br> - Was an applied example of the method presented? <br> - Was the example's research design described enough to understand the analysis? <br> - Was the example's analysis presented (at least in brief)? <br> - Did the presentation offer a good critical appraisal of the quality of the research (especially the applied method)?",
             "<b>4. Conclusion</b> <br> - Were the main points of the presentation summarised? <br> - Did the conclusion describe (at least briefly) how one might apply the method? <br> - Were any points for discussion mentioned or questions from the audience answered?",
             "<b>5. Spoken presentation</b> <br> - Were the speakers loud enough to be heard at the back? <br> - Were they <b>speaking to the audience</b>, speaking freely (best) or rather only reading off notes (okay) or reading off the slides (worst)?",
             "<b>6. Visual presentation</b> <br> - Were the presentation materials (slides) clear? <br> - Were any graphics shown readable? <br> - Were any slides overcrowded with text?") #,
  #present=c("","","","","",""),
  # evaluation=c("","","","","","")
)

colnames(rub)<-c(# "Block",
                 "Criteria and Indicators" #,
                 #"yes/no/partial/NA",
                 #"Evaluation")
)

# kable(plan, format = "latex")  # For LaTeX output
# kable(plan, format = "html")   # For HTML output

rub %>% 
  # group_by(Block) %>% 
  kable("html", escape = FALSE) %>% 
  # collapse_rows(1, valign="middle") %>% 
  kable_styling(full_width = FALSE) # %>% 
  # column_spec(1, bold = TRUE) %>% 
  # collapse_rows(1, valign="middle") # %>% column_spec(2, width = "80px") %>% 
  # column_spec(2, width = "120px")

```

:::

## Examination (Klausur)

<!-- PAST QUESTIONS: -->
<!-- 2024-5 -->
<!-- - What elements do social movement strategies consist of? How do different strategies seek to effect change? Discuss with examples. -->
<!-- - Why do movement organisations form coalitions; what are the advantages and risks? What factors (within organisations, between organisations, and contextually) influence whether movement organisations form coalitions?  -->
<!-- - What are three theories that explain why movements emerge, how they act, and whether they have an impact? Describe one concept from each theory and why it is important for understanding social movements.  -->
<!-- - How do movements frame issues? What different sorts of frames are used? Why are they important for movements?	 -->
<!-- - A core feature of social movements is that they generate a 'collective identity' among their members. What is collective identity, what does it consist of, how is it produced, and why is it important for movements?  -->
<!-- - How can movements impact politics and society? Discuss with examples. -->

<!-- 2023-4 -->
<!-- - How do movements emerge? What key concepts help to understand how some people come together in a movement to engage in collective action?  -->
<!-- - How do movements frame issues? What different sorts of frames are used? Why are they important for movements? -->
<!-- - Movements often provoke responses from state and/or other social actors. Describe (with examples) how state actors can respond to movements; and describe (with examples) how other social actors (such as countermovements) can respond to movements.  -->
<!-- - Why do people participate in movements? Consider the 'collective action problem' and how both individuals and (social movement) organisations are relevant to explaining why people participate.  -->
<!-- - A core feature of social movements is that they generate a 'collective identity' among their members. What is collective identity, what does it consist of, how is it produced, and why is it important for movements?  -->
<!-- - How can movements impact politics and society? Discuss with examples. -->

Students will not have an examination in this course, but they will in the '**Einführung Politisches System der BRD**' course. During that examination, they will respond to one of three essay questions based on the content of this course.

### Information on examination

Typically, the examination is conducted over 90 minutes and will take the following form: for the lecture ('**Einführung Politisches System der BRD**') portion, students will be given five short answer (i.e., one or two paragraphs) questions; they should respond to three of the five. For the seminar (Grundkurs) portion, students will be given three essay prompts and they should respond to one of them. 

For this course, students might receive an essay prompt like the following: *What does the term 'political opportunity structure' mean? How does it help us understand how movements emerge and (potentially) have an impact? Discuss with examples*. 

A good response to this prompt (and others) would likely consist of four parts: (1) Broad introductory response; (2) Elaborate in (sufficient) detail to answer the questions; (3) Describe examples; (4) Concluding summary.

(1) **Broad introductory response**, e.g.:   
    - Political opportunity structure (POS) refers to availabilities of resources, institutional arrangements, and histories of mobilisation that shape (facilitating/hindering) movement activity. Different aspects of these components are relevant to different movements. But POS in all cases is an important part of explaining if and how movements form, how they operate, and whether and what kinds of impacts they can have. ...
  
(2) **Elaborate in (sufficient) detail to answer the questions**, e.g.:   
    - POS defines what resources are available for emergent movements to use, whether they can access the public sphere and/or political decision-making, and whether there are viable models of mobilisation and campaigning. While individuals and groups always have some possibility of exercising their agency, the structure referred to by POS is a powerful constraining set of factors. ...

(3) **Describe examples**, e.g.:   
    - At a most basic level, POS can refer to the freedom for movements to form, to mobilise and campaign for certain goals. Authoritarian states typically restrict this freedom and offer less space for movements than in liberal democratic states like Germany. Looking closely at specific examples can demonstrate how POS shapes movements. The anti-nuclear movement in Germany, for example, benefited by forming in the wake of 1968-era mobilisations, so models existed for mobilising. Germany’s federal state structure presented more ‘opportunities’ for movements to disrupt implementation of nuclear projects. Critical events, such as Cold War missile installation and the Chernobyl accident, strengthened the movement. And Germany’s (PR) electoral system made the creation of a political party (i.e., institutionalisation and creation of elite allies) a viable option. Germany’s virtually non-existent nuclear power infrastructure is evidence of the anti-nuclear movements success in Germany, contrasted with less successful movement activity in, e.g., France. ...
    
(4) **Concluding summary**, e.g.:    
    - To assess whether and in what ways movements can emerge, whether and in what ways movements can have an impact, it is essential to consider relevant POS aspects. Movements exercise their agency within the limitations created by POS.

## Essay (*Hausarbeit*)

Students that are required by their degree programme to write a final essay will write an analytical data report on a social movement phenomenon, such as protest activity (or in a specific country, or in a sub-national area) or online posting activity by a social movement organisation(s). The report should be 2000-3000 words (excluding citations). It should briefly introduce the subject, briefly discuss relevant research literature, and (particularly important) **should gather and present (in a tablular and/or graphic format) some data relevant to understanding the social movement phenomenon** (e.g., a report on a social movement group might present protest events associated with that group; or a report on online activity might present the quantity and characteristics of online posts by the platform account associated with a group(s)). Please note that introduction and literature review are to be *brief*. **The intention of this report is for you to gather data and generate analytical insights**. Imagine that you are describing this social movement phenomenon to someone (a policymaker or researcher) with no specific knowledge of it; your job is to provide context briefly, offer specific knowledge, and why that knowledge is important. 

Students are generally free to choose their topic and have it confirmed by the instructor---though the instructor may veto a topic and assign another, or ask the student to choose another. At least one rule applies: **no drawing any data from or citing Statista or other data curation services**. <!-- By the middle of the semester, students should have started their data collection and should submit a draft dataframe: this (most likely) will be an Excel file with your variables in columns and observations in rows. The instructor will check it and offer any necessary guidance about completing data collection. --> Prior to the end of the semester, students intending to write the essay should submit a one-page synopsis that states your topic, lists some relevant research sources, describes the parameters of the data (i.e., variables, number of observations---think of writing up a mini-codebook) and presents a few example rows (i.e., observations), lists any ideas on how to present the data (i.e., how you will visualise it in your report), and identifies any particular points on which you need preliminary feedback. (**This is your chance to get risk-free feedback on your work. Embrace it!**) Feedback on the synopsis may direct students to revise their topic, focus on other sources, and/or reconsider their data approach to their proposed report.

<!-- Deadline for draft dataframe submission: **`r SemesterEnd - (35)`** -->

Deadline for short synopsis submission: **[`r SemesterEnd - (21)`]{style="color:red;"}**

Deadline for full report submission (including full dataframe): **[`r SemesterEnd + (28)`]{style="color:red;"}**

Due to time constraints, no written preliminary feedback can be provided after the synopsis submission deadline. Students requesting such feedback will receive the following response: "Unfortunately, I am unable to provide feedback at this time. But I suggest you look at the assignment description, the scoring rubric, and the example data report---all provided on the course website."

Under exceptional circumstances, the instructor may accept late submissions of the full report due to unforeseen circumstances. Generally, late submissions will be marked down 0,3 for every two days it is not submitted. If foreseen circumstances make the deadline impossible, please speak to the instructor to make an alternative arrangement. 

An [example data report](../report/index.qmd) is provided on this website. It is a slightly modified version of a previous student's submission and shows an example of a very good data report.

Finally, a suggested (purely voluntary, but perhaps to your ultimate benefit) mode of conducting work on your report: students may find it advantageous to work in [R](https://www.r-project.org/about.html) and [Rstudio](https://posit.co/download/rstudio-desktop/). This is a powerful data management and analysis tool. It combines the capability to import and visualise data, conduct sophisticated analyses, and even present them in nicely formatted documents (whether Word, PDF, or HTML). Students interested in working with datasets in their theses, going on to advanced academic studies, or pursuing a career in research will benefit enormously from engaging with this tool early and often. The course introduction will provide some tips for using this tool. For further information, please turn to the vast material related to R online or inquire with the instructor. Nevertheless, [students are free to work with whatever tools they are most comfortable with, including Microsoft Office programmes.]{style="color:red;"}

**Once you have read this far: please send me an email before second class stating your favourite city and what (if any) politically violent groups you are particularly interested in learning about.**

::: {.callout-caution collapse="true"}
## Scoring rubric

```{r rep-rubric, echo=FALSE}
#| message: false
#| warning: false
#| paged-print: false
# Load necessary library
library(dplyr)
library(kableExtra)

rubric <- data.frame(
  # block=c("Content", "Content", "Content", "Content", "Form", "Form"),
  criteria=c("<b>1. Introduction</b> <br> - Does the introduction clearly introduce the topic and related data? <br> - Does the introduction briefly state any information or context that is essential to understanding the topic and/or data? <br> - Does the introduction state the aim of the report? <br> - Does the introduction summarise the structure of the report and the main findings?",
             "<b>2. Literature and concepts</b> <br> - Does the report have a section on relevant literature and concepts related to their topic and data? <br> - Does the section provide detailed systematised concept(s) to understand the rest of the data report? <br> - Does the section provide the contextual information necessary to understand the rest of the data report?", 
             "<b>3. Data description</b> <br> - Does the data description explain how the data were collected or created? <br> - Does the data description report the (most important) variables and overall data structure (e.g., one row is an observation of what)? <br> Does the data description provide any necessary descriptive statistics (e.g., number of observations, range/mean/median, missing observations)? <br> - Does the data description reflect on the strengths and weaknesses of the underlying source of the data?",
             "<b>4. Data presentation</b> <br> - Are the data presented in a tabular and graphical format? <br> - Is the presentation readable and readily interpretable (e.g., clear labels, legends)? <br> - Is the presentation directly connected to the analytical discussion?",
             "<b>5. Analytical insights</b> <br> - Does the report discuss (descriptive) analytical insights enabled by presentation of the data and closer inspection of certain data points or collections of data points? <br> - Is the report cautious about the limits of how much we can interpret the data (e.g., how certain can we be of any trends; how plausible is any speculation about causes?)?",
             "<b>6. Conclusion</b> <br> - Does the conclusion summarise the report? <br> - Does it reflect on the shortcomings or limitations of the data and interpretation? <br> - Does it discuss possible ways that this data might be used further (e.g., for thesis research projects, to inform policy discussions)?",
             "<b>7. Form</b> <br> - Is the report well-organised, logically structured, and easy to follow? <br> - Do the different sections clearly, coherently relate to each other? <br> - Is the writing clear, with few if any spelling, typological, grammatical, or syntactical errors?",
             "<b>8. Data</b> <br> - Has the report been submitted with the raw data? <br> - Is the data file clear? <br> - Would the reader be able to replicate the data report using the data file?") #, 
  # present=c("","","","","",""),
  # evaluation=c("","","","","","")
)

colnames(rubric)<-c("Criteria and Indicators")

# kable(plan, format = "latex")  # For LaTeX output
# kable(plan, format = "html")   # For HTML output

rubric %>% 
  # group_by(Block) %>% 
  kable("html", escape = FALSE) %>% 
  # collapse_rows(1, valign="middle") %>% 
  kable_styling(full_width = FALSE) # %>% 
  # column_spec(1, bold = TRUE) %>% 
  # collapse_rows(1, valign="middle") # %>% column_spec(2, width = "80px") %>% 
  # column_spec(2, width = "120px")

```

:::

<!-- ## Exercise (*Übungsaufgabe*) -->

<!-- Students that are required by their degree programme to complete an exercise will write a memo on an assigned far-right actor (e.g., a party, movement, or organisation). The memo topic will be assigned during our 12th class meeting, on **\textcolor{red}{`r MeetingDays$Date[12]`}** and it will be due on the day before our 13th class meeting **\textcolor{red}{`r MeetingDays$Date[13] - 1`}**. Under exceptional circumstances, the instructor may accept late submissions due to unforeseen circumstances. Generally, late submissions will be marked down 0,3 for every two days it is not submitted. If foreseen circumstances make the deadline inconvenient, please speak to the instructor to make an alternative arrangement.  -->

<!-- The memo should be 1000-2000 words. It should provide a basic description of the far-right actor and any important context. It should gather and present (in a table and/or graphic format) some data relevant to understanding the far-right actor (e.g., a memo on a party might present their election results in the last five national elections; a memo on a movement might present the protest events they have organised during a specific period of time). Imagine that you are describing this far-right actor to someone (a policymaker or researcher) with no specific knowledge of it; your job is to provide context, specific knowledge, and why that knowledge is important.  -->

<!-- Possible far-right actors: Reichsbürger,  -->

<!-- ## Klausur -->

<!-- # Useful books and sources of information. -->


# Student conduct

## Plagiarism

Plagiarism is when ideas and words from others are presented as if they are one's own. It does not matter from which source (e.g., a book, magazine, newspaper, or the internet) the ideas and text came from or whether it is a large or small piece or whether it is copied verbatim or rephrased. The only consequential point is whether the original source is correctly cited or not.

